---
title: "Bangladesh Food Diary"
author: "Mari Roberts"
date: "2/10/2020"
output: pdf_document
---

```{r}
# set wd
mydirectory <- "/Users/mari/internship/AgricultureModel/Datasets"

# load necessary packages
requiredPackages = c('foreign', # read dta
                     'dplyr',
                     'haven',
                     'readr') 

for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}

# read in each dta file
filenames <- list.files(path="Datasets", pattern=".*dta")
setwd(mydirectory)
for (i in 1:length(filenames)){
  assign(filenames[i], read_dta(paste("", filenames[i], sep=''))
  )}
}
# remove NAs from HH members
# hh_all <- HouseholdComposition_members_level_2.dta %>% filter(currentposition != "NA")

hh_all <- HouseholdComposition_members_level_2.dta %>% select(hh_ID,
                                                              member_1_ID,
                                                              hhm_occu_type,
                                                              hhm_occupation,
                                                              canStandOwn = hhm_health1,
                                                              canWalk5Km = hhm_health2,
                                                              canCarry20L = hhm_health3)

# factor variables
hh_all$hhm_occu_type <- as.factor(hh_all$hhm_occu_type)
hh_all$hhm_occupation <- as.factor(hh_all$hhm_occupation)
# hh_all$canStandOwn <- as.factor(hh_all$canStandOwn)
# hh_all$canWalk5Km <- as.factor(hh_all$canWalk5Km)
# hh_all$canCarry20L <- as.factor(hh_all$canCarry20L)
# str(hh_all)

get_mode <- function(x){
  return(names(sort(table(x), decreasing = T, na.last = T)[1:10]))
}

# top occupations
get_mode(hh_all$hhm_occupation)

# top occupation types
get_mode(hh_all$hhm_occu_type)
```

*Top occupations:*
Raising poultry  	farming = 443
Raising livestock  	farming = 372
Animal Breeder  	livestock = 223
Small trader (roadside stand or stall)  	trader = 112
Agricultural day labor  	wage = 97
Farming = 76
Student  	nonearning = 64
Service (private sector )  	salaried = 53
Small industry  	prod = 42
Veterinary/paravet doctor  	livestock = 30

*Top occupation types:*
"nonearning" = 945
"farming" = 299
"trader" = 166
"salaried" = 150
"wage" = 124

*Health Measures*

0 = No
1 = Yes
77 = Don't know

Combined 0 and 77 

```{r}
# differences in hh count and reported members in health measures
# hh_tally <- hh_subset %>% group_by(hh_ID) %>% tally()
# hh_report <- HouseholdComposition_level_1.dta %>% select(hh_ID, n=hh_members)
# which(duplicated(hh_report) | duplicated(hh_report[nrow(hh_report):1, ])[nrow(hh_report):1])
hh_count <- HouseholdComposition_level_1.dta %>% select(hh_ID, hh_members) 
# reporting differences between hh_members throughout the year, likely deaths and births
# hh_distinct <- hh_count %>% distinct(hh_ID, .keep_all = TRUE)
# remove 101004 for now???
# hh_count <- hh_count %>% filter(hh_ID != "101004")
hh_count <- hh_count %>% distinct(hh_ID, .keep_all = TRUE)

# combine 0 and 77 ("no" and "don't know")
hh_all <- hh_all %>% mutate(canCarry20La = ifelse(canCarry20L==77 | canCarry20L==0, 0, 1),
                                canWalk5Kma = ifelse(canWalk5Km==77 | canWalk5Km==0, 0, 1),
                                canStandOwna = ifelse(canStandOwn==77 | canStandOwn==0, 0, 1))

# count health measures per household
hh_subset <- hh_all %>% select(hh_ID, canCarry20La, canWalk5Kma, canStandOwna)
          carry <- hh_subset %>% group_by(hh_ID) %>% tally(canCarry20La)
          walk <- hh_subset %>% group_by(hh_ID) %>% tally(canWalk5Kma)
          stand <- hh_subset %>% group_by(hh_ID) %>% tally(canStandOwna)

# determine percentage of health measure per household
hh_cleaned <- merge(hh_count, carry, by = "hh_ID") 
hh_cleaned <- merge(hh_cleaned, walk, by = "hh_ID") 
hh_cleaned <- merge(hh_cleaned, stand, by = "hh_ID") 
hh_cleaned <- hh_cleaned %>% select(hh_ID,
                                    hh_members,
                                    canCarry20L = n.x,
                                    canWalk5Km = n.y,
                                    canStandOwn = n) %>% 
                             mutate(pctCanCarry20L = canCarry20L/hh_members,
                                    pctCanWalk5Km = canWalk5Km/hh_members,
                                    pctCanStandOwn = canStandOwn/hh_members)

# remove percentages above 100, differences in number of members
hh_final <- hh_cleaned %>% filter(pctCanCarry20L <= 1 &
                                  pctCanWalk5Km <= 1 &
                                  pctCanStandOwn <= 1)

View(hh_final)
```

```{r}
foodDiary <- `34.FoodDiary_food_level_2.dta` %>% select(hh_ID, food_grp_namec)
table(foodDiary$food_grp_namec)                                                   
```

                      cereals          dairy         drinks      fishlarge 
            80           3492            309            158           1182 
     fishsmall         fruits       leafyveg        meategg            oil 
           959            488           1504           2279           1373 
otherfoodohome         pulses         spices     vegetables 
           140           1648            234           3058 

```{r}
food_subset <- foodDiary %>% select(hh_ID, food_grp_namec)

food <- food_subset %>%
  group_by(hh_ID, food_grp_namec) %>%
  summarise(n = n()) 

# food1 %>% group_by(hh_ID, food_grp_namec) %>% summarise(Value = max(Value))
food_summary <- food %>% group_by(hh_ID, food_grp_namec) %>% summarise(n = max(n))
```


