---
title: "PCA"
author: "Mari Roberts"
date: "4/7/2020"
output: pdf_document
---

```{r}
# load necessary packages
requiredPackages = c('foreign', # read dta
                     'dplyr',
                     'haven',
                     'gridExtra',
                     'readr',
                     'dummies',
                     'tidyverse') # missing values using map
# only downloads packages if needed
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}

# mydirectory <- "/Users/mari/AgricultureModel/Datasets"
# setwd(mydirectory)
# filenames <- list.files(path=mydirectory, pattern=".*dta")
# df..list <- lapply(filenames, read_dta)
#      list..res <- lapply(list(df..list), 
#                 function(x) setDT(x)[,lapply(.SD,function(x) {  
#          list(.N,sum(is.na(x)))}),by=hh_ID][,`:=`(index=1:.N,type=c("count", 
#                                                               "no..na")),hh_ID])
#      Reduce(function(x,y) merge(x,y,by=c("hh_ID","type","index")), list..res)

# set wd
mydirectory <- "/Users/mari/AgricultureModel/Datasets"
setwd(mydirectory)

filenames <- list.files(path=mydirectory, pattern=".*dta")

# read in each dta file
filenames <- list.files(path=mydirectory, pattern=".*dta")
for (i in 1:length(filenames)){
  assign(filenames[i], read_dta(paste("", filenames[i], sep=''))
  )}

# response rates, NAs, counts
df_counts_NAs <- list.files(path=mydirectory, pattern=".*dta") %>%
  map(~{
    read_dta(.x) %>%
      group_by(hh_ID) %>%
      summarize_all(.funs = list(count = ~n(), NAs = ~sum(is.na(.))))
  }) %>%
  reduce(full_join)
```

# Questions Asked Once

## Health and Demographics

View(Basicinformation.dta) - age religion

```{r}
##########################
# Health by Person
##########################

hh_count <- HouseholdComposition_level_1.dta %>% select(hh_ID, member_1_ID, hh_members) 
# reporting differences between hh_members throughout the year, likely deaths and births?
hh_count <- hh_count %>% distinct(hh_ID, .keep_all = TRUE)

hh_all <- HouseholdComposition_members_level_2.dta %>% mutate(height_meters = tot_height_inch*0.0254,
                                                              canStandOwn = hhm_health1,
                                                              canWalk5Km = hhm_health2,
                                                              canCarry20L = hhm_health3)

# BMI categories
hh_all <- hh_all %>% mutate(bmi = (weight_kg/(height_meters^2)))

# remove outliers for weight and height
hh_all <- hh_all %>% filter(tot_height_inch >= 1 & tot_height_inch <= 100)
hh_all <- hh_all %>% filter(weight_kg >= 1 & weight_kg <= 100)

hh_all <- hh_all %>% mutate(bmiCategory = ifelse(bmi >= 30, "obese", 
                                          ifelse(bmi >=25, "overweight", 
                                          ifelse(bmi >=18.5, "normal", 
                                          ifelse(bmi < 18.5, "underweight", NA)))))

# combine 0 and 77 ("no" and "don't know")
hh_all <- hh_all %>% mutate(canCarry20La = ifelse(canCarry20L==77 | canCarry20L==0, 0, 1),
                            canWalk5Kma = ifelse(canWalk5Km==77 | canWalk5Km==0, 0, 1),
                            canStandOwna = ifelse(canStandOwn==77 | canStandOwn==0, 0, 1))

# 0 = male, 1 = female 
# BMI (metric) = 1.3 x weight (kg) / height (m)^2.5
hh_all <- hh_all %>% mutate(sex = ifelse(hhm_sex == 1,0,1)) %>% 
                       select(hh_ID,
                              member_1_ID,
                              hhm_relation,
                              sex,
                              age = hhm_age,
                              maritalStatus = marital_status,
                              literacy,
                              education,
                              attendingCollege = hhm_attending,
                              occupationType = hhm_occu_type,
                              canCarry20L = canCarry20La,
                              canWalk5Km = canWalk5Kma,
                              canStandOwn = canStandOwna,
                              bmi,
                              bmiCategory)

# factor variables
hh_all$sex = factor(hh_all$sex)
hh_all$maritalStatus = factor(hh_all$maritalStatus)
hh_all$literacy = factor(hh_all$literacy)
hh_all$education = factor(hh_all$education)
hh_all$occupationType = factor(hh_all$occupationType)
hh_all$bmiCategory = factor(hh_all$bmiCategory)

# logical variables
hh_all$attendingCollege = factor(hh_all$attendingCollege)
hh_all$canCarry20L = factor(hh_all$canCarry20L)
hh_all$canWalk5Km = factor(hh_all$canWalk5Km)
hh_all$canStandOwn = factor(hh_all$canStandOwn)

####################
# Data by resondents
####################
hh_respondent <- hh_all %>% filter(hhm_relation == 1)

##########################
# Health by Household
##########################

# count health measures per household
hh_subset <- hh_all %>% select(hh_ID, member_1_ID, bmi, canCarry20La, canWalk5Kma, canStandOwna)
          carry <- hh_subset %>% group_by(hh_ID) %>% tally(canCarry20La)
          walk <- hh_subset %>% group_by(hh_ID) %>% tally(canWalk5Kma)
          stand <- hh_subset %>% group_by(hh_ID) %>% tally(canStandOwna)

# determine percentage of health measure per household
hh_health <- merge(hh_count, carry, by = "hh_ID") 
hh_health <- merge(hh_health, walk, by = "hh_ID") 
hh_health <- merge(hh_health, stand, by = "hh_ID") 
hh_health <- hh_health %>% select(hh_ID,
                                    member_1_ID,
                                    hh_members,
                                    canCarry20L = n.x,
                                    canWalk5Km = n.y,
                                    canStandOwn = n) %>% 
                             mutate(pctCanCarry20L = canCarry20L/hh_members,
                                    pctCanWalk5Km = canWalk5Km/hh_members,
                                    pctCanStandOwn = canStandOwn/hh_members)

# remove percentages above 100, differences in number of members
hh_health <- hh_health %>% filter(pctCanCarry20L <= 1 &
                                  pctCanWalk5Km <= 1 &
                                  pctCanStandOwn <= 1) %>% select(-canCarry20L,-canWalk5Km,-canStandOwn)

# children


```

# PCA

PCA allows you to see the overall "shape" of the data, identifying which samples are similar to one another and which are very different. This can enable us to identify groups of samples that are similar and work out which variables make one group different from another.

```{r}
# housing characteristics
housing_all <- `41. HousingandSanitation.dta` 

# respondent input year instead of years old
housing_fix_year <- housing_all %>% arrange(desc(house_old))
housing_fix_year <- head(housing_fix_year, 19)
housing_fix_year <- housing_fix_year %>% select(hh_ID, house_old, today)
housing_fix_year$today <- as.Date(housing_fix_year$today, "%b %d, %Y")
housing_fix_year$submissionyear <- as.numeric(format(housing_fix_year$today,'%Y'))
housing_fix_year<- housing_fix_year %>% mutate(house_age = submissionyear-house_old) %>% select(hh_ID, house_age)

housing_all_not_fix_year <- housing_all %>% filter(hh_ID != 115161 &
                                        hh_ID != 120230 &
                                        hh_ID != 105055 &
                                        hh_ID != 221250 &
                                        hh_ID != 233386 &
                                        hh_ID != 120238 &
                                        hh_ID != 222252 &
                                        hh_ID != 240474 &
                                        hh_ID != 108087 &
                                        hh_ID != 120228 &
                                        hh_ID != 230349 &
                                        hh_ID != 235414 &
                                        hh_ID != 231368 &
                                        hh_ID != 115165 &
                                        hh_ID != 235407 &
                                        hh_ID != 229339 &
                                        hh_ID != 224284 &
                                        hh_ID != 232370) %>% select(hh_ID, house_old)

housing_all_not_fix_year <- housing_all_not_fix_year %>% mutate(house_age = house_old) %>% select(-house_old)
housing_all_years_fixed <- merge(housing_all_not_fix_year, housing_fix_year, by = c("hh_ID"), all=TRUE)
housing_all_years_fixed <- housing_all_years_fixed %>% select(hh_ID, house_age = house_age.x)

housing_all <- housing_all %>% select(hh_ID,
                                      cellphone,
                                      house_sharing, 
                                      housewall_material, 
                                      housewall_material_other, 
                                      houseroof_material, 
                                      houseroof_material_other, 
                                      housefloor_material, 
                                      housefloor_material_other, 
                                      house_rooms, 
                                      house_rooms_sleeping, 
                                      house_elec, 
                                      house_supply_off, 
                                      fuel_source, 
                                      fuel_source_other, 
                                      lighting_source, 
                                      latrine_type, 
                                      latrine_other, 
                                      water_supply, 
                                      water_other_purpose, 
                                      water_other, 
                                      drinking_source_same, 
                                      drinking_source, 
                                      drinking_other, 
                                      water_purify, 
                                      water_purify_other, 
                                      handpump, 
                                      garbage, 
                                      garbage_other)

housing_all <- merge(housing_all_years_fixed, housing_all, by = c("hh_ID"))

# all data asked once
final_data <- merge(housing_all, hh_health, by = "hh_ID")

# map missing values
# map(final_data, ~sum(is.na(.)))

# remove columns with all NAs and nested questions 
final_data <- final_data[,colSums(is.na(final_data))<nrow(final_data)]
final_data <- final_data %>% select(-member_1_ID,
                                    -water_purify_other, 
                                    -fuel_source_other,
                                    -drinking_source,
                                    -house_supply_off,
                                    -water_other_purpose)

# add FAKE caloric count data
final_data$caloricFake <- rnorm(269, mean=2000, sd=50)

# factor variables
final_data$housewall_material <- factor(final_data$housewall_material)
final_data$houseroof_material <- factor(final_data$houseroof_material)
final_data$housefloor_material <- factor(final_data$housefloor_material)
final_data$house_elec <- factor(final_data$house_elec)
final_data$fuel_source <- factor(final_data$fuel_source)
final_data$lighting_source <- factor(final_data$lighting_source)
final_data$latrine_type <- factor(final_data$latrine_type)
final_data$water_supply <- factor(final_data$water_supply)
final_data$drinking_source_same <- factor(final_data$drinking_source_same)
final_data$water_purify <- factor(final_data$water_purify)
final_data$garbage <- factor(final_data$garbage)

str(final_data)
```

```{r}
###################################################################################################
# VIEW
###################################################################################################
View(final_data)
View(hh_respondent)
```


# PCA
https://uc-r.github.io/pca

```{r}
new_data <- dummy.data.frame(final_data, names = c("housewall_material","houseroof_material","housefloor_material","house_elec","fuel_source","lighting_source","latrine_type","water_supply","drinking_source_same","water_purify","garbage"))
str(new_data)
new_data <- new_data %>% select(-hh_ID)

scaled_df <- apply(new_data, 2, scale)
head(scaled_df)

# remove NAs
row.has.na <- apply(scaled_df, 1, function(x){any(is.na(x))})
final.filtered <- scaled_df[!row.has.na,]

hh.cov <- cov(final.filtered)
hh.eigen <- eigen(hh.cov)
str(hh.eigen)

# Extract the loadings
(phi <- hh.eigen$vectors[,1:2])

phi <- -phi
row.names(phi) <- c("house_age","cellphone","house_sharing","housewall_material1", "housewall_material2","housewall_material3","housewall_material4","housewall_material5","houseroof_material1",
"houseroof_material2","houseroof_material3","houseroof_material4","houseroof_material5","houseroof_material6",
"houseroof_material7","housefloor_material1","housefloor_material2","housefloor_material3","housefloor_material4",
"housefloor_material5","housefloor_material99", "house_rooms","house_rooms_sleeping","house_elec0",
"house_elec1","fuel_source1","fuel_source2","fuel_source3","fuel_source4",
"fuel_source5","fuel_source6","fuel_source7","fuel_source8","fuel_source9",
"fuel_source99","lighting_source1","lighting_source3","lighting_source4","lighting_source5",
"lighting_source99","latrine_type1","latrine_type2","latrine_type3","latrine_type4",
"latrine_type5","latrine_type6","latrine_type99","water_supply0","water_supply1",
"drinking_source_same0","drinking_source_same1" ,"water_purify1","water_purify2","water_purify3",
"water_purify4","water_purify5","water_purify99","garbage1","garbage2",
"garbage3","garbage4","garbage5","garbage6","garbage7",
"garbage8","hh_members","pctCanCarry20L","pctCanWalk5Km","pctCanStandOwn",
"caloricFake")
colnames(phi) <- c("PC1", "PC2")

# Calculate Principal Components scores
PC1 <- as.matrix(scaled_df) %*% phi[,1]
PC2 <- as.matrix(scaled_df) %*% phi[,2]

# Create data frame with Principal Components scores
PC <- data.frame(hh_ID = row.names(final_data), PC1, PC2)
head(PC)

# Plot Principal Components for each HH
PCAplot <- ggplot(PC, aes(PC1, PC2)) + 
  modelr::geom_ref_line(h = 0) +
  modelr::geom_ref_line(v = 0) +
  geom_text(aes(label = hh_ID), size = 3) +
  xlab("First Principal Component") + 
  ylab("Second Principal Component") + 
  ggtitle("First Two Principal Components of HH Data")
PCAplot
```

```{r}
pca_result <- prcomp(final.filtered, scale = FALSE)
names(pca_result)
# means
pca_result$center
# standard deviations
pca_result$scale
# provides the principal component loadings
pca_result$rotation 
pca_result$rotation <- -pca_result$rotation
pca_result$rotation

pca_result$x <- - pca_result$x
head(pca_result$x)

biplot(pca_result, scale = 0)
```

```{r}
pca_result$sdev # standard deviation of each principal component
VE <- pca_result$sdev^2 # variance explained by each principal component is obtained by squaring these values

# proportion of variance explained by each principal component
PVE <- VE / sum(VE)
round(PVE, 2)
```

 [1] 0.07 0.06 0.05 0.04 0.04 0.03 0.03 0.03 0.03 0.03 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.01
[30] 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.00 0.00 0.00 0.00 0.00 0.00 0.00
[59] 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00











# Agriculture 

01. AgriculturalExtensionServices.dta
02. AgriculturalProduction_level_1.dta
03. AgriculturalProduction_plot_repeat_begin_level_2.dta
04. AgriculturalProduction_crop_level_3.dta
06. AgriculturalSubsidyCard.dta

```{r}

agriculture <- `01. AgriculturalExtensionServices.dta`

# agriculture_NAs <- agriculture %>%
#   group_by(hh_ID) %>% 
#   summarize_all(.funs = list(count = ~n(), NAs = ~sum(is.na(.))))


```

###07. BadShocks_level_1.dta
###08. BadShocks_event_repeat_level_2.dta

###09. ClimateEvent.dta

###10. Cosmetics_level_1.dta
###11. Cosmetics_item_repeat_level_2.dta

###12. Crops_level_1.dta
###13. Crops_plot_repeat_begin_level_2.dta
###14. Crops_crop_level_3.dta
###15. Crops_group_crop_i_croptype_level_4.dta

###16. CurrentMigrants_level_1.dta
###17. CurrentMigrants_begin_repeat_mig_level_2.dta

###18. DrinkingWater_level_1.dta
###19. DrinkingWater_source_level_2.dta

###20. Facilities_level_1.dta
###21. Facilities_facility_repeat_level_2.dta

###22. FertilizersAndPesticides_level_1.dta
###23. FertilizersAndPesticides_plot_repeat_begin_level_2.dta
###24. FertilizersAndPesticides_crop_level_3.dta
###25. FertilizersAndPesticides_group_crop_i_croptype_level_4.dta
###26. FertilizersAndPesticides_rep_fert_level_5.dta

###27. FishPondInputs_level_1.dta
###28. FishPondInputs_begin_level_2.dta
###29. FishPondProduction_level_1.dta
###30. FishPondProduction_pond_begin_repeat_level_2.1.dta
###31. FishPondProduction_river_repeat_level_2.2.dta
###32. FishPondProduction_fish_repeat_level_3.dta

###33. FoodDiary_level_1.dta
###34. FoodDiary_food_level_2.dta
###35. Fooddiary_food_foodtype_level_3.dta
###36. FoodStorageCapacity.dta

###37. FuelLighting_level_1.dta
###38. FuelLighting_item_repeat_level_2.dta

###39. GoodShocks_level_1.dta
###40. GoodShocks_event_repeat_level_2.dta

###41. HousingandSanitation.dta

###42. InformationTools_level_1.dta
###43. InformationTools_tech_level_2.dta
###44. InformationTools_tech_use_level_3.dta

###45. Irrigation_level_1.dta
###46. Irrigation_plot_repeat_begin_level_2.dta
###47. Irrigation_crop_level_3.dta
###48. Irrigation_group_crop_i_crop_repeat_type_level_4.dta

###49. Livestock_level_1.dta
###50. Livestock_animal_level_2.dta

###51. Loans_level_1.dta
###52. Loans_each_loan_level_2.dta

###53. Marketing_level_1.dta
###54. Marketing_sellrell_prod_repeat_level_2.dta

###55. MobileInternet_level_1.dta
###56. MobileInternet_app_use_level_2.dta

###57. NonAgriculturalEnterprise_level_1.dta
###58. NonAgriculturalEnterprise_buss_level_2.dta

###59. OtherIncome_level_1.dta

###60. OtherIncome_income_level_2.dta

###61. RemittanceIn_level_1.dta
###62. RemittanceIn_begin_repeat_mig_level_2.dta
###63. RemittanceOut_level_1.dta
###64. RemittanceOut_begin_repeat_mig_level_2.dta

###65. SafetyProgram_level_1.dta
###66. SafetyProgram_event_repeat_level_2.dta

###67. Savings_level_1.dta
###68. Savings_each_savings_level_2.dta

###69. SubjectiveWellbeing.dta

###70. TransportTravel_level_1.dta
###71. TransportTravel_item_repeat_level_2.dta
###72. TransportationTools_level_1.dta
###73. TransportationTools_transport_level_2.dta
###74. TransportationTools_transport_use_level_3.dta

###75. WashingCleaning_level_1.dta
###76. WashingCleaning_item_repeat_level_2.dta

###77. WorkAnimals_level_1.dta
###78. WorkAnimals_animals_level_2.dta
###79. WorkAnimals_animals_use_level_3.dta

###80. employment_level_1.dta
###81. employment_work_done_level_2.dta

###82. farmLabor_level_1.dta
###83. farmLabor_begin_repeat_plot_level_2.dta
###84. farmLabor_labor_repeat_level_3.dta

###85. illness_level_1.dta
###86. illness_was_ill_level_2.dta

###87. latrineUse.dta
###88. latrineWalk_level_1.dta
###89. latrineWalk_begin_repeat_lat_level_2.dta

###90. rentingToolsMachAn_level_1.dta
###91. rentingToolsMachAn_plot_repeat_begin_level_2.dta
###92. rentingToolsMachAn_crop_level_3.dta
###93. rentingToolsMachAn_group_crop_i_crop_repeat_type_level_4.dta

###94. schoolAttendance_level_1.dta
###95. schoolAttendance_missed_school_level_2.dta

###96. tubewellWalk_level_1.dta
###97. tubewellWalk_begin_repeat_tw_level_2.dta