---
title: "Economic Well-Being in Bagladesh"
author: "Mari Roberts"
date: "4/7/2020"
output: pdf_document
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# load necessary packages
requiredPackages = c('foreign', # read dta
                     'dplyr',
                     'haven',
                     'gridExtra',
                     'readr',
                     'dummies',
                     'data.table',
                     'ggplot2', # plots
                     'tidyverse') # missing values using map
# only downloads packages if needed
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}

# set wd
mydirectory <- "/Users/mari/AgricultureModel/Datasets"
setwd(mydirectory)

filenames <- list.files(path=mydirectory, pattern=".*dta")

# read in each dta file
filenames <- list.files(path=mydirectory, pattern=".*dta")
for (i in 1:length(filenames)){
  assign(filenames[i], read_dta(paste("", filenames[i], sep=''))
  )}

# response rates, NAs, counts
# df_counts_NAs <- list.files(path=mydirectory, pattern=".*dta") %>%
#   map(~{
#     read_dta(.x) %>%
#       group_by(hh_ID) %>%
#       summarize_all(.funs = list(count = ~n(), NAs = ~sum(is.na(.))))
#   }) %>%
#   reduce(full_join)
```

# Questions Asked Once

```{r include=FALSE}
####################################################
## Health and Demographics
####################################################

##########################
# Basic Info
##########################

# respondent_info <- Basicinformation.dta %>% select(hh_ID,
#                                                    hh_head, # relationship to head of household
#                                                    religion,
#                                                    age)
# remove outliers for age
# respondent_info <- respondent_info %>% filter(age <= 100)

#209 1 Self
 # 31 2 Spouse
 # 57 3 Child
 # 7  4 Sibling
 # 143 5 Parent

 # 374 1 Muslim
 # 72 2 Hindu
 # 1 4 Buddhist

hh_count <- HouseholdComposition_level_1.dta %>% select(hh_ID, member_1_ID, hh_members) 
# reporting differences between hh_members throughout the year, likely deaths and births?
hh_count <- hh_count %>% distinct(hh_ID, .keep_all = TRUE)

hh_all <- HouseholdComposition_members_level_2.dta %>% mutate(height_meters = tot_height_inch*0.0254,
                                                              canStandOwn = hhm_health1,
                                                              canWalk5Km = hhm_health2,
                                                              canCarry20L = hhm_health3)

# BMI categories
hh_all <- hh_all %>% mutate(bmi = (weight_kg/(height_meters^2)))

# remove outliers for weight and height
hh_all <- hh_all %>% filter(tot_height_inch >= 1 & tot_height_inch <= 100)
hh_all <- hh_all %>% filter(weight_kg >= 1 & weight_kg <= 100)

hh_all <- hh_all %>% mutate(bmiCategory = ifelse(bmi >= 30, "obese", 
                                          ifelse(bmi >=25, "overweight", 
                                          ifelse(bmi >=18.5, "normal", 
                                          ifelse(bmi < 18.5, "underweight", NA)))))

# combine 0 and 77 ("no" and "don't know")
hh_all <- hh_all %>% mutate(canCarry20L = ifelse(canCarry20L==77 | canCarry20L==0, 0, 1),
                            canWalk5Km = ifelse(canWalk5Km==77 | canWalk5Km==0, 0, 1),
                            canStandOwn = ifelse(canStandOwn==77 | canStandOwn==0, 0, 1))

# 0 = male, 1 = female 
# BMI (metric) = 1.3 x weight (kg) / height (m)^2.5
hh_all <- hh_all %>% mutate(sex = ifelse(hhm_sex == 1,0,1)) %>% 
                       select(hh_ID,
                              member_1_ID,
                              hhm_relation,
                              sex,
                              age = hhm_age,
                              maritalStatus = marital_status,
                              literacy,
                              education,
                              attendingCollege = hhm_attending,
                              occupationType = hhm_occu_type,
                              canCarry20L,
                              canWalk5Km,
                              canStandOwn,
                              bmi,
                              bmiCategory)

# factor variables
hh_all$sex = factor(hh_all$sex)
hh_all$maritalStatus = factor(hh_all$maritalStatus)
hh_all$literacy = factor(hh_all$literacy)
hh_all$education = factor(hh_all$education)
hh_all$occupationType = factor(hh_all$occupationType)
hh_all$bmiCategory = factor(hh_all$bmiCategory)

# logical variables
# hh_all$attendingCollege = factor(hh_all$attendingCollege)
# hh_all$canCarry20L = factor(hh_all$canCarry20L)
# hh_all$canWalk5Km = factor(hh_all$canWalk5Km)
# hh_all$canStandOwn = factor(hh_all$canStandOwn)

# does hh have children?
hh_all <- hh_all %>% mutate(isChild = ifelse(age>=18, 0, 1))
hh_children <- hh_all %>% group_by(hh_ID) %>% tally(isChild)
hh_children <- hh_children %>% mutate(numChildren = n) %>% select(hh_ID, numChildren)

# merge
hh_all <- merge(hh_children, hh_all, by = "hh_ID")
  
##########################
# Data by resondents
##########################
hh_respondent <- hh_all %>% filter(hhm_relation == 1)

##########################
# Health by Household
##########################

# count health measures per household
hh_subset <- hh_all %>% select(hh_ID, member_1_ID, bmi, canCarry20L, canWalk5Km, canStandOwn)
          carry <- hh_subset %>% group_by(hh_ID) %>% tally(canCarry20L)
          walk <- hh_subset %>% group_by(hh_ID) %>% tally(canWalk5Km)
          stand <- hh_subset %>% group_by(hh_ID) %>% tally(canStandOwn)

# determine percentage of health measure per household
hh_health <- merge(hh_count, carry, by = "hh_ID") 
hh_health <- merge(hh_health, walk, by = "hh_ID") 
hh_health <- merge(hh_health, stand, by = "hh_ID") 
hh_health <- hh_health %>% select(hh_ID,
                                    member_1_ID,
                                    hh_members,
                                    canCarry20L = n.x,
                                    canWalk5Km = n.y,
                                    canStandOwn = n) %>% 
                             mutate(pctCanCarry20L = canCarry20L/hh_members,
                                    pctCanWalk5Km = canWalk5Km/hh_members,
                                    pctCanStandOwn = canStandOwn/hh_members)

# remove percentages above 100, differences in number of members
hh_health <- hh_health %>% filter(pctCanCarry20L <= 1 &
                                  pctCanWalk5Km <= 1 &
                                  pctCanStandOwn <= 1) %>% select(-canCarry20L,-canWalk5Km,-canStandOwn)

hh_char <- merge(hh_health, hh_children, by = "hh_ID")
hh_char <- hh_char %>% select(-member_1_ID)

# TRUE, if there are no duplicates in hh_ID
length(unique(hh_char$hh_ID)) == nrow(hh_char)
```

```{r}
####################################################
## Housing Characteristics
####################################################

# housing and sanitation characteristics
housing_all <- `41. HousingandSanitation.dta` 


# 113148 120225 221250 224277 more than one entry
# probably need to figure out how to get rid of these. Max date?????????
# housing_all$hh_ID[duplicated(housing_all$hh_ID)]
# housing_all <- housing_all %>% filter(hh_ID != 113148 &
#                                       hh_ID != 120225 &
#                                       hh_ID != 221250 &
#                                       hh_ID != 224277)

##########
# if there is a hh_ID duplicate, use the first entry
##########
# TRUE, if there are no duplicates in hh_ID
length(unique(housing_all$hh_ID)) == nrow(housing_all)
housing_all$submissiondate <- as.Date(housing_all$submissiondate, "%b %d, %Y")
housing_all <- setDT(housing_all)[housing_all[, .I[which.min(submissiondate)], by=hh_ID]$V1]
housing_all <- housing_all %>% select(-submissiondate)
##########

# respondent input year instead of years old
housing_fix_year <- housing_all %>% arrange(desc(house_old))
housing_fix_year <- head(housing_fix_year, 19)
housing_fix_year <- housing_fix_year %>% select(hh_ID, house_old, today)
housing_fix_year$today <- as.Date(housing_fix_year$today, "%b %d, %Y")
housing_fix_year$submissionyear <- as.numeric(format(housing_fix_year$today,'%Y'))
housing_fix_year<- housing_fix_year %>% mutate(house_age = submissionyear-house_old) %>% select(hh_ID, house_age)

housing_all_not_fix_year <- housing_all %>% filter(hh_ID != 115161 &
                                        hh_ID != 120230 &
                                        hh_ID != 105055 &
                                        hh_ID != 221250 &
                                        hh_ID != 233386 &
                                        hh_ID != 120238 &
                                        hh_ID != 222252 &
                                        hh_ID != 240474 &
                                        hh_ID != 108087 &
                                        hh_ID != 120228 &
                                        hh_ID != 230349 &
                                        hh_ID != 235414 &
                                        hh_ID != 231368 &
                                        hh_ID != 115165 &
                                        hh_ID != 235407 &
                                        hh_ID != 229339 &
                                        hh_ID != 224284 &
                                        hh_ID != 232370) %>% select(hh_ID, house_old)

housing_all_not_fix_year <- housing_all_not_fix_year %>% mutate(house_age = house_old) %>% select(-house_old)
housing_all_years_fixed <- merge(housing_all_not_fix_year, housing_fix_year, by = c("hh_ID"), all=TRUE)
housing_all_years_fixed <- housing_all_years_fixed %>% select(hh_ID, house_age = house_age.x)

housing_all <- housing_all %>% select(-sanitation_1_ID,-expiration_date,
                                      -max_submissions,-task_value,-task_length,-recall,
                                      -recall_length,-crowdsource,-week_number,-start_time,
                                      -end_time, -today, -start_date)

housing_all <- merge(housing_all_years_fixed, housing_all, by = c("hh_ID"))

####################################################
## Latrine and Water
####################################################

latrine_all <- `87. latrineUse.dta` %>% select(hh_ID, submissiondate, use_lat, main_use, count_latrine, pct_open)

##########
# if there is a hh_ID duplicate, use the first entry
##########
latrine_all$submissiondate <- as.Date(latrine_all$submissiondate, "%b %d, %Y")
latrine_all <- setDT(latrine_all)[latrine_all[, .I[which.min(submissiondate)], by=hh_ID]$V1]
latrine_all <- latrine_all %>% select(-submissiondate)
##########

housing_all <- merge(latrine_all, housing_all, by = c("hh_ID"))

housing_all$hh_ID[duplicated(housing_all$hh_ID)]

####################################################
## Non-agricultural enterprise
####################################################

# Anyone in household owned/operated any business in 12 months?
nonagricultural_enterprise <- `57. NonAgriculturalEnterprise_level_1.dta` %>% select(hh_ID, submissiondate, business)

##########
# if there is a hh_ID duplicate, use the first entry
##########
nonagricultural_enterprise$submissiondate <- as.Date(nonagricultural_enterprise$submissiondate, "%b %d, %Y")
nonagricultural_enterprise <- setDT(nonagricultural_enterprise)[nonagricultural_enterprise[, .I[which.min(submissiondate)], by=hh_ID]$V1]
nonagricultural_enterprise <- nonagricultural_enterprise %>% select(-submissiondate)
##########

# merge with household characteristics
housing_all <- merge(nonagricultural_enterprise, housing_all, by = c("hh_ID"))
housing_all$hh_ID[duplicated(housing_all$hh_ID)]
str(housing_all)

#################
# ordered factor variables
#################

housing_all$pct_open <- factor(housing_all$pct_open, ordered = TRUE)
# What kind of toilet facility do members of your household use most of the time?
housing_all$main_use <- factor(housing_all$main_use, ordered = TRUE)
# house wall, roof, and floor
housing_all$housewall_material <- factor(housing_all$housewall_material, ordered = TRUE)
housing_all$houseroof_material <- factor(housing_all$houseroof_material, ordered = TRUE)
housing_all$housefloor_material <- factor(housing_all$housefloor_material, ordered = TRUE)

####################################################
## Facilities
####################################################

facilities <- `20. Facilities_level_1.dta` %>% select(hh_ID,submissiondate, facilities,fac_count)

# there are too many variations on the types of facilities visited, so change to:
# visits health centers, bazaar, local shops
facilities$visits_healthcenter <- ifelse(grepl("1",facilities$facilities), 1, 0)
facilities$visits_bazaar <- ifelse(grepl("6",facilities$facilities), 1, 0)
facilities$visits_localshop <- ifelse(grepl("5",facilities$facilities), 1, 0)
facilities <- facilities %>% select(-facilities)

##########
# if there is a hh_ID duplicate, use the first entry
##########
facilities$submissiondate <- as.Date(facilities$submissiondate, "%b %d, %Y")
facilities <- setDT(facilities)[facilities[, .I[which.min(submissiondate)], by=hh_ID]$V1]
facilities <- facilities %>% select(-submissiondate)
##########

# merge with household characteristics
housing_all <- merge(facilities, housing_all, by = c("hh_ID"))

housing_all$hh_ID[duplicated(housing_all$hh_ID)]

####################################################
## Plots
####################################################

plots <- Plots_plot_level_2.dta # fix year
temp <- plots_level_1.dta %>% select(hh_ID, submissiondate, plot_1_ID, today) 
plots <- merge(plots, temp, by=c("hh_ID","plot_1_ID"))

plots$today <- format(as.Date(plots$today, format="%b %d, %Y"),"%Y")
plots$yr_acq <- format(as.Date(plots$yr_acq, format="%b %d, %Y"),"%Y")  
plots$today <- as.numeric(plots$today)
plots$yr_acq <- as.numeric(plots$yr_acq)
plots$plot_age <- plots$today - plots$yr_acq 

# too many plot types (change to three types)
plots$plot_type_homestead <- ifelse(grepl("1",plots$plot_type), 1, 0)
temp <- c("2","8")
plots$plot_type_cultivable_land_pond <- ifelse(grepl(paste(temp, collapse = "|"),plots$plot_type), 1, 0)
temp <- c("3","4","5","6","7","9"," ")
plots$plot_type_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$plot_type), 1, 0)

# who_owns - too many factor levels (change to three types)
plots$who_owns_male <- ifelse(grepl("1",plots$who_owns), 1, 0)
plots$who_owns_family <- ifelse(grepl("2",plots$who_owns), 1, 0)
temp <- c("3","4","5","6")
plots$who_owns_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_owns), 1, 0)

# who_owns_off - too many factor levels (change to three types)
plots$who_owns_off_male <- ifelse(grepl("1",plots$who_owns_off), 1, 0)
plots$who_owns_off_family <- ifelse(grepl("2",plots$who_owns_off), 1, 0)
temp <- c("3","4","5","6")
plots$who_owns_off_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_owns_off), 1, 0)
 
# who_decision - too many factor levels (change to three types)
plots$who_decision_male <- ifelse(grepl("1",plots$who_decision), 1, 0)
plots$who_decision_family <- ifelse(grepl("2",plots$who_decision), 1, 0)
temp <- c("3","4","5","6")
plots$who_decision_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_decision), 1, 0)

# who_responsible - not enough responses

# who_dec_spd - too many factor levels (change to three types)
plots$who_dec_spd_male <- ifelse(grepl("1",plots$who_dec_spd), 1, 0)
plots$who_dec_spd_family <- ifelse(grepl("2",plots$who_dec_spd), 1, 0)
temp <- c("3","4","5","6")
plots$who_dec_spd_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_dec_spd), 1, 0)

# who_infra - too many factor levels (change to three types)
plots$who_infra_male <- ifelse(grepl("1",plots$who_infra), 1, 0)
plots$who_infra_family <- ifelse(grepl("2",plots$who_infra), 1, 0)
temp <- c("3","4","5","6")
plots$who_infra_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_infra), 1, 0)

##########
# if there is a hh_ID duplicate, use the first entry
##########
# 100+ duplicates
plots$hh_ID[duplicated(plots$hh_ID)]
plots$submissiondate <- as.Date(plots$submissiondate, "%b %d, %Y")
plots <- setDT(plots)[plots[, .I[which.min(submissiondate)], by=hh_ID]$V1]
plots <- plots %>% select(-submissiondate)
##########

plots <- plots %>%  select( hh_ID,
                            plot_type_homestead,
                            plot_type_cultivable_land_pond,
                            plot_type_other,
                            size_plot,
                            flood_depth, # wrong units probably
                            dis_from_home,
                            soil_type,
                            cur_opr_status,
                            amt_rec,
                            cur_mv,
                            how_acq,
                            plot_age,
                            plot_use,
                            work_last_seas,
                            # In last 12 months, who decided to build any infrastructure on this plot?
                            who_infra_male,
                            who_infra_family,
                            who_infra_other,
                            # Who uses the plot?  
                            who_owns_male,
                            who_owns_family,
                            who_owns_other,
                            # Who officially owns?
                            who_owns_off_male,
                            who_owns_off_family,
                            who_owns_off_other,
                            # who_decision who takes most decisions regarding type of crop to be planted or fish to be raised?
                            who_decision_male,
                            who_decision_family,
                            who_decision_other,
                            # who decides how to spend revenues generated from crops or fish?
                            who_dec_spd_male,
                            who_dec_spd_family,
                            who_dec_spd_other)

# merge with household characteristics
housing_all <- merge(plots, housing_all, by = c("hh_ID"))
housing_all$hh_ID[duplicated(housing_all$hh_ID)]
```

## Remove nested and NA questions
```{r}
housing_cleaned <- housing_all %>% select(-rent_paid, 
                                          -drinking_source, 
                                          -house_supply_off, 
                                          -house_elec_cost, 
                                          -fuel_source_other,
                                          -drinking_source, 
                                          -water_purify_other, 
                                          -arsenic_check, 
                                          #-water_purpose_other, 
                                          -color_check)

# remove variables with most missing values
housing_cleaned <- housing_cleaned %>% select(-work_last_seas, 
                                              #-who_responsible, 
                                              -housewall_material_other, 
                                              -houseroof_material_other, 
                                              -housefloor_material_other, 
                                              -lighting_source_other, 
                                              -latrine_other, 
                                              -water_other, 
                                              -drinking_other, 
                                              -garbage_other, 
                                              -amt_rec,
                                              -handpump)

# map(housing_cleaned, ~sum(is.na(.)))
# 
# View(housing_cleaned)

hh_data <- merge(housing_cleaned, hh_char, by = "hh_ID")
hh_data$hh_ID[duplicated(hh_data$hh_ID)]
```

```{r}
categorical_variables <- hh_data %>% select(-size_plot, 
                                                    -flood_depth, 
                                                    -dis_from_home, 
                                                    -cur_mv, 
                                                    -plot_age, 
                                                    -count_latrine, 
                                                    -rent_estimate, 
                                                    -house_old,
                                                    -fuel_cost, 
                                                    -lighting_cost, 
                                                    -cell_cost, 
                                                    -house_rooms, 
                                                    -house_rooms_sleeping,
                                                    -house_age, 
                                                    -fac_count,
                                                    -numChildren,
                                                    -pctCanCarry20L,
                                                    -pctCanWalk5Km,
                                                    -pctCanStandOwn,
                                                    -hh_members,
                                                    -count_latrine)
continuous_variables <- hh_data %>% select(hh_ID, size_plot, 
                                                    flood_depth, 
                                                    dis_from_home, 
                                                    cur_mv, 
                                                    plot_age, 
                                                    count_latrine, 
                                                    rent_estimate, 
                                                    house_old,
                                                    fuel_cost, 
                                                    lighting_cost, 
                                                    cell_cost, 
                                                    house_rooms, 
                                                    house_rooms_sleeping,
                                                    house_age, 
                                                    fac_count,
                                                    numChildren,
                                                    pctCanCarry20L,
                                                    pctCanWalk5Km,
                                                    pctCanStandOwn,
                                                    hh_members,
                                                    count_latrine)
##################################
# factor variables
##################################

# convert variables to factor variables except hh_ID (column 1)
str(categorical_variables)
categorical_variables[,-1] <- lapply(categorical_variables[,-1], function(x) as.factor(as.character(x)))

# merge categorical and continous variables into one dataframe
final_hh_data <- inner_join(categorical_variables, continuous_variables, by ="hh_ID")










dummy_categorical_variables <- dummy.data.frame(categorical_variables)
str(dummy_categorical_variables)

dummy_continuous_variables <- dummy.data.frame(continuous_variables)
str(dummy_continuous_variables)


# Create dummy variables from x6
# for(level in unique(x6)){
#     data[paste("dummy", level, sep = "_")] <- ifelse(x6 == level, 1, 0)
# }

final_data <- merge(dummy_categorical_variables,dummy_continuous_variables, by="hh_ID")
final_data <- final_data %>% mutate_if(is.numeric,as.factor)

# Correlation matrix with appropriate coefficients
# Pearson product-moment: 2 continuous variables
# Point-biserial: 1 continuous and 1 binary variable
# Phi: 2 binary variables
# For testing purposes use hetcor function
library(polycor)
C <- as.matrix(hetcor(data=final_data))

# Run PCA
pca <- princomp(covmat=C)
L <- loadings(pca)

# Calculate Scores
scores <- data * L
```






Weighting?, time variable
zscore standardize ->weighting factor -> sensitivity analysis ---- diff weights

divide of collective households?
explain differences
collective management leads to XYZ

TEST
compare variation - crowdsource vs respondent on one question


IDEA

"many tasks included a 'crowdsourcing' component, in which the respondent would complete the task first for him- or herself, and then repeat the task for any friend, neighbor, or passerby; these participants were ideally selected on an approximately random basis ... The purpose of the crowdsourcing component in the study was to examine whether a crowdsourced sample might demonstrate a reduced selection bias, and thus better approximate a true representative sample, than our purposive sample of potential early adopters."

how similar the sample is to the crowdsourced one 
- Select characteristics (e.g., age, gender, literacy, education, etc.) and even in terms of responses to a select number of questions.  

If the personal characteristics are highly similar between the two samples, it may be that as suggested, selection bias is not reduced by crowdsourcing in this way and that, therefore, this particular type of crowdsourced sample does not yield a better approximation of a true representative sample as intended. 
- Look at the distributions of the two samples in terms of these demographics, etc. and see which one better reflects the population to see which one is more representative.  

Hypothesis: Individuals selected by respondents because they are friends, neighbors, or passersby, would tend to be similar in traits to the respondents and not provide the protection against selection bias that is proposed. 


-----only crowdsourced sample has years of education
----crowdsource might not be same every time










# PCA

PCA allows you to see the overall "shape" of the data, identifying which samples are similar to one another and which are very different. This can enable us to identify groups of samples that are similar and work out which variables make one group different from another.

https://uc-r.github.io/pca

```{r}
new_data <- dummy.data.frame(final_data, names = c("housewall_material","houseroof_material","housefloor_material","house_elec","fuel_source","lighting_source","latrine_type","water_supply","drinking_source_same","water_purify","garbage"))
str(new_data)
new_data <- new_data %>% select(-hh_ID)

scaled_df <- apply(new_data, 2, scale)
head(scaled_df)

# remove NAs
row.has.na <- apply(scaled_df, 1, function(x){any(is.na(x))})
final.filtered <- scaled_df[!row.has.na,]

hh.cov <- cov(final.filtered)
hh.eigen <- eigen(hh.cov)
str(hh.eigen)

# Extract the loadings
(phi <- hh.eigen$vectors[,1:2])

phi <- -phi
row.names(phi) <- c("house_age","cellphone","house_sharing","housewall_material1", "housewall_material2","housewall_material3","housewall_material4","housewall_material5","houseroof_material1",
"houseroof_material2","houseroof_material3","houseroof_material4","houseroof_material5","houseroof_material6",
"houseroof_material7","housefloor_material1","housefloor_material2","housefloor_material3","housefloor_material4",
"housefloor_material5","housefloor_material99", "house_rooms","house_rooms_sleeping","house_elec0",
"house_elec1","fuel_source1","fuel_source2","fuel_source3","fuel_source4",
"fuel_source5","fuel_source6","fuel_source7","fuel_source8","fuel_source9",
"fuel_source99","lighting_source1","lighting_source3","lighting_source4","lighting_source5",
"lighting_source99","latrine_type1","latrine_type2","latrine_type3","latrine_type4",
"latrine_type5","latrine_type6","latrine_type99","water_supply0","water_supply1",
"drinking_source_same0","drinking_source_same1" ,"water_purify1","water_purify2","water_purify3",
"water_purify4","water_purify5","water_purify99","garbage1","garbage2",
"garbage3","garbage4","garbage5","garbage6","garbage7",
"garbage8","hh_members","pctCanCarry20L","pctCanWalk5Km","pctCanStandOwn",
"caloricFake")
colnames(phi) <- c("PC1", "PC2")

# Calculate Principal Components scores
PC1 <- as.matrix(scaled_df) %*% phi[,1]
PC2 <- as.matrix(scaled_df) %*% phi[,2]

# Create data frame with Principal Components scores
PC <- data.frame(hh_ID = row.names(final_data), PC1, PC2)
head(PC)

# Plot Principal Components for each HH
PCAplot <- ggplot(PC, aes(PC1, PC2)) + 
  modelr::geom_ref_line(h = 0) +
  modelr::geom_ref_line(v = 0) +
  geom_text(aes(label = hh_ID), size = 3) +
  xlab("First Principal Component") + 
  ylab("Second Principal Component") + 
  ggtitle("First Two Principal Components of HH Data")
PCAplot
```

```{r}
pca_result <- prcomp(final.filtered, scale = FALSE)
names(pca_result)
# means
pca_result$center
# standard deviations
pca_result$scale
# provides the principal component loadings
pca_result$rotation 
pca_result$rotation <- -pca_result$rotation
pca_result$rotation

pca_result$x <- - pca_result$x
head(pca_result$x)

biplot(pca_result, scale = 0)
```

```{r}
pca_result$sdev # standard deviation of each principal component
VE <- pca_result$sdev^2 # variance explained by each principal component is obtained by squaring these values

# proportion of variance explained by each principal component
PVE <- VE / sum(VE)
round(PVE, 2)
```

 [1] 0.07 0.06 0.05 0.04 0.04 0.03 0.03 0.03 0.03 0.03 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.02 0.01
[30] 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.01 0.00 0.00 0.00 0.00 0.00 0.00 0.00
[59] 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00 0.00

ordered factor variables
recode dummies









# Agriculture 

01. AgriculturalExtensionServices.dta
02. AgriculturalProduction_level_1.dta
03. AgriculturalProduction_plot_repeat_begin_level_2.dta
04. AgriculturalProduction_crop_level_3.dta
06. AgriculturalSubsidyCard.dta

```{r}

agriculture <- `01. AgriculturalExtensionServices.dta`

# agriculture_NAs <- agriculture %>%
#   group_by(hh_ID) %>% 
#   summarize_all(.funs = list(count = ~n(), NAs = ~sum(is.na(.))))


```

###07. BadShocks_level_1.dta
###08. BadShocks_event_repeat_level_2.dta

###09. ClimateEvent.dta

###10. Cosmetics_level_1.dta
###11. Cosmetics_item_repeat_level_2.dta

###12. Crops_level_1.dta
###13. Crops_plot_repeat_begin_level_2.dta
###14. Crops_crop_level_3.dta
###15. Crops_group_crop_i_croptype_level_4.dta

###16. CurrentMigrants_level_1.dta
###17. CurrentMigrants_begin_repeat_mig_level_2.dta

###18. DrinkingWater_level_1.dta
###19. DrinkingWater_source_level_2.dta

###20. Facilities_level_1.dta
###21. Facilities_facility_repeat_level_2.dta

###22. FertilizersAndPesticides_level_1.dta
###23. FertilizersAndPesticides_plot_repeat_begin_level_2.dta
###24. FertilizersAndPesticides_crop_level_3.dta
###25. FertilizersAndPesticides_group_crop_i_croptype_level_4.dta
###26. FertilizersAndPesticides_rep_fert_level_5.dta

###27. FishPondInputs_level_1.dta
###28. FishPondInputs_begin_level_2.dta
###29. FishPondProduction_level_1.dta
###30. FishPondProduction_pond_begin_repeat_level_2.1.dta
###31. FishPondProduction_river_repeat_level_2.2.dta
###32. FishPondProduction_fish_repeat_level_3.dta

###33. FoodDiary_level_1.dta
###34. FoodDiary_food_level_2.dta
###35. Fooddiary_food_foodtype_level_3.dta
###36. FoodStorageCapacity.dta

###37. FuelLighting_level_1.dta
###38. FuelLighting_item_repeat_level_2.dta

###39. GoodShocks_level_1.dta
###40. GoodShocks_event_repeat_level_2.dta

###41. HousingandSanitation.dta

###42. InformationTools_level_1.dta
###43. InformationTools_tech_level_2.dta
###44. InformationTools_tech_use_level_3.dta

###45. Irrigation_level_1.dta
###46. Irrigation_plot_repeat_begin_level_2.dta
###47. Irrigation_crop_level_3.dta
###48. Irrigation_group_crop_i_crop_repeat_type_level_4.dta

###49. Livestock_level_1.dta
###50. Livestock_animal_level_2.dta

###51. Loans_level_1.dta
###52. Loans_each_loan_level_2.dta

###53. Marketing_level_1.dta
###54. Marketing_sellrell_prod_repeat_level_2.dta

###55. MobileInternet_level_1.dta
###56. MobileInternet_app_use_level_2.dta

###57. NonAgriculturalEnterprise_level_1.dta
###58. NonAgriculturalEnterprise_buss_level_2.dta

###59. OtherIncome_level_1.dta

###60. OtherIncome_income_level_2.dta

###61. RemittanceIn_level_1.dta
###62. RemittanceIn_begin_repeat_mig_level_2.dta
###63. RemittanceOut_level_1.dta
###64. RemittanceOut_begin_repeat_mig_level_2.dta

###65. SafetyProgram_level_1.dta
###66. SafetyProgram_event_repeat_level_2.dta

###67. Savings_level_1.dta
###68. Savings_each_savings_level_2.dta

###69. SubjectiveWellbeing.dta

###70. TransportTravel_level_1.dta
###71. TransportTravel_item_repeat_level_2.dta
###72. TransportationTools_level_1.dta
###73. TransportationTools_transport_level_2.dta
###74. TransportationTools_transport_use_level_3.dta

###75. WashingCleaning_level_1.dta
###76. WashingCleaning_item_repeat_level_2.dta

###77. WorkAnimals_level_1.dta
###78. WorkAnimals_animals_level_2.dta
###79. WorkAnimals_animals_use_level_3.dta

###80. employment_level_1.dta
###81. employment_work_done_level_2.dta

###82. farmLabor_level_1.dta
###83. farmLabor_begin_repeat_plot_level_2.dta
###84. farmLabor_labor_repeat_level_3.dta

###85. illness_level_1.dta
###86. illness_was_ill_level_2.dta

###87. latrineUse.dta
###88. latrineWalk_level_1.dta
###89. latrineWalk_begin_repeat_lat_level_2.dta

###90. rentingToolsMachAn_level_1.dta
###91. rentingToolsMachAn_plot_repeat_begin_level_2.dta
###92. rentingToolsMachAn_crop_level_3.dta
###93. rentingToolsMachAn_group_crop_i_crop_repeat_type_level_4.dta

###94. schoolAttendance_level_1.dta
###95. schoolAttendance_missed_school_level_2.dta

###96. tubewellWalk_level_1.dta
###97. tubewellWalk_begin_repeat_tw_level_2.dta