---
title: "Economic Well-Being in Bagladesh"
author: "Mari Roberts"
date: "4/7/2020"
output: pdf_document
---

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# load necessary packages
requiredPackages = c('foreign', # read dta
                     'dplyr', # data manipulation
                     'haven',
                     'gridExtra', # data manipulation
                     'readr', # read files
                     'readxl',# read files
                     'dummies', # PCA
                     'lubridate', # data manipulation
                     'data.table', # data manipulation
                     'FactoMineR', # PCA
                     'factoextra', # PCA
                     'lattice', # plots
                     'ggplot2', # plots
                     'tidyverse') # missing values using map
# only downloads packages if needed
for(p in requiredPackages){
  if(!require(p,character.only = TRUE)) install.packages(p)
  library(p,character.only = TRUE)
}

# set wd
mydirectory <- "/Users/mari/AgricultureModel/Datasets"
setwd(mydirectory)

filenames <- list.files(path=mydirectory, pattern=".*dta")

# read in each dta file
filenames <- list.files(path=mydirectory, pattern=".*dta")
for (i in 1:length(filenames)){
  assign(filenames[i], read_dta(paste("", filenames[i], sep=''))
  )}
```

# Questions Asked Once

```{r include=FALSE}
####################################################
## Health and Demographics
####################################################

##########################
# Basic Info
##########################

# find number of hh members for calculations later
hh_count <- HouseholdComposition_level_1.dta %>% select(hh_ID, member_1_ID, hh_members) 
hh_count <- hh_count %>% distinct(hh_ID, .keep_all = TRUE)

# rename variables
hh_all <- HouseholdComposition_members_level_2.dta %>% mutate(height_meters = tot_height_inch*0.0254,
                                                              canStandOwn = hhm_health1,
                                                              canWalk5Km = hhm_health2,
                                                              canCarry20L = hhm_health3)

# BMI categories
hh_all <- hh_all %>% mutate(bmi = (weight_kg/(height_meters^2)))

# remove outliers for weight and height
hh_all <- hh_all %>% filter(tot_height_inch >= 1 & tot_height_inch <= 100)
hh_all <- hh_all %>% filter(weight_kg >= 1 & weight_kg <= 100)

# create BMI categories
hh_all <- hh_all %>% mutate(bmiCategory = ifelse(bmi >= 30, "obese", 
                                          ifelse(bmi >=25, "overweight", 
                                          ifelse(bmi >=18.5, "normal", 
                                          ifelse(bmi < 18.5, "underweight", NA)))))

# combine 0 and 77 ("no" and "don't know")
hh_all <- hh_all %>% mutate(canCarry20L = ifelse(canCarry20L==77 | canCarry20L==0, 0, 1),
                            canWalk5Km = ifelse(canWalk5Km==77 | canWalk5Km==0, 0, 1),
                            canStandOwn = ifelse(canStandOwn==77 | canStandOwn==0, 0, 1))

# 0 = male, 1 = female 
# select demographic variables
hh_all <- hh_all %>% mutate(sex = ifelse(hhm_sex == 1,0,1)) %>% 
                       select(hh_ID,
                              member_1_ID,
                              hhm_relation,
                              sex,
                              age = hhm_age,
                              maritalStatus = marital_status,
                              literacy,
                              education,
                              attendingCollege = hhm_attending,
                              occupationType = hhm_occu_type,
                              canCarry20L,
                              canWalk5Km,
                              canStandOwn,
                              bmi,
                              bmiCategory)

# change into factor variables
hh_all$sex = factor(hh_all$sex)
hh_all$maritalStatus = factor(hh_all$maritalStatus)
hh_all$literacy = factor(hh_all$literacy)
hh_all$education = factor(hh_all$education)
hh_all$occupationType = factor(hh_all$occupationType)
hh_all$bmiCategory = factor(hh_all$bmiCategory)

# does hh have children?
hh_all <- hh_all %>% mutate(isChild = ifelse(age>=18, 0, 1))
hh_children <- hh_all %>% group_by(hh_ID) %>% tally(isChild)
hh_children <- hh_children %>% mutate(numChildren = n) %>% select(hh_ID, numChildren)

# merge datasets
hh_all <- merge(hh_children, hh_all, by = "hh_ID")
  
##########################
# Data by resondents
##########################

# data about respondents
hh_respondent <- hh_all %>% filter(hhm_relation == 1)

##########################
# Health by Household
##########################

# count health measures per household
hh_subset <- hh_all %>% select(hh_ID, member_1_ID, bmi, canCarry20L, canWalk5Km, canStandOwn)
          carry <- hh_subset %>% group_by(hh_ID) %>% tally(canCarry20L)
          walk <- hh_subset %>% group_by(hh_ID) %>% tally(canWalk5Km)
          stand <- hh_subset %>% group_by(hh_ID) %>% tally(canStandOwn)

# determine percentage of health measure per household
hh_health <- merge(hh_count, carry, by = "hh_ID") 
hh_health <- merge(hh_health, walk, by = "hh_ID") 
hh_health <- merge(hh_health, stand, by = "hh_ID") 
hh_health <- hh_health %>% select(hh_ID,
                                    member_1_ID,
                                    hh_members,
                                    canCarry20L = n.x,
                                    canWalk5Km = n.y,
                                    canStandOwn = n) %>% 
                             mutate(pctCanCarry20L = canCarry20L/hh_members,
                                    pctCanWalk5Km = canWalk5Km/hh_members,
                                    pctCanStandOwn = canStandOwn/hh_members)

# remove percentages above 100, differences in number of members
hh_health <- hh_health %>% filter(pctCanCarry20L <= 1 &
                                  pctCanWalk5Km <= 1 &
                                  pctCanStandOwn <= 1) %>% select(-canCarry20L,-canWalk5Km,-canStandOwn)

hh_char <- merge(hh_health, hh_children, by = "hh_ID")
hh_char <- hh_char %>% select(-member_1_ID)

# TRUE, if there are no duplicates in hh_ID
# length(unique(hh_char$hh_ID)) == nrow(hh_char)
```

```{r}
####################################################
## Housing Characteristics
####################################################

# housing and sanitation characteristics
housing_all <- `41. HousingandSanitation.dta` 

##########
# if there is a hh_ID duplicate, use the first entry
# question was only supposed to be answered once but some households submitted twice
##########
# TRUE, if there are no duplicates in hh_ID
# length(unique(housing_all$hh_ID)) == nrow(housing_all)
housing_all$submissiondate <- as.Date(housing_all$submissiondate, "%b %d, %Y")
housing_all <- setDT(housing_all)[housing_all[, .I[which.min(submissiondate)], by=hh_ID]$V1]
housing_all <- housing_all %>% select(-submissiondate)
##########

# respondent input year instead of years old
# determine house age
housing_fix_year <- housing_all %>% arrange(desc(house_old))
housing_fix_year <- head(housing_fix_year, 19)
housing_fix_year <- housing_fix_year %>% select(hh_ID, house_old, today)
housing_fix_year$today <- as.Date(housing_fix_year$today, "%b %d, %Y")
housing_fix_year$submissionyear <- as.numeric(format(housing_fix_year$today,'%Y'))
housing_fix_year<- housing_fix_year %>% mutate(house_age = submissionyear-house_old) %>% select(hh_ID, house_age)
housing_all_not_fix_year <- housing_all %>% filter(hh_ID != 115161 &
                                        hh_ID != 120230 &
                                        hh_ID != 105055 &
                                        hh_ID != 221250 &
                                        hh_ID != 233386 &
                                        hh_ID != 120238 &
                                        hh_ID != 222252 &
                                        hh_ID != 240474 &
                                        hh_ID != 108087 &
                                        hh_ID != 120228 &
                                        hh_ID != 230349 &
                                        hh_ID != 235414 &
                                        hh_ID != 231368 &
                                        hh_ID != 115165 &
                                        hh_ID != 235407 &
                                        hh_ID != 229339 &
                                        hh_ID != 224284 &
                                        hh_ID != 232370) %>% select(hh_ID, house_old)
housing_all_not_fix_year <- housing_all_not_fix_year %>% mutate(house_age = house_old) %>% select(-house_old)
housing_all_years_fixed <- merge(housing_all_not_fix_year, housing_fix_year, by = c("hh_ID"), all=TRUE)
housing_all_years_fixed <- housing_all_years_fixed %>% select(hh_ID, house_age = house_age.x)

# select variables
housing_all <- housing_all %>% select(-sanitation_1_ID,-expiration_date,
                                      -max_submissions,-task_value,-task_length,-recall,
                                      -recall_length,-crowdsource,-week_number,-start_time,
                                      -end_time, -today, -start_date, -house, -house_old)

# merge datasets
housing_all <- merge(housing_all_years_fixed, housing_all, by = c("hh_ID"))

# water_purify - too many factor levels
housing_all <- housing_all %>% mutate(does_water_purify = ifelse(water_purify==1, 0, 1))

# garbage - too many factor levels
housing_all <- housing_all %>% mutate(garbage_collected = ifelse(garbage==1|garbage==2, 1, 0))

# lighting_source - too many factor levels - What is your main source of lighting fuel?
housing_all <- housing_all %>% mutate(lighting_source_elec = ifelse(lighting_source==1 | lighting_source==3, 1, 0))

# fuel_source - too many factor levels - What is your main source of cooking fuel?
housing_all <- housing_all %>% mutate(fuel_source_wood = ifelse(fuel_source==5, 1, 0))

# housing materials - too many factor levels, combine smaller levels
housing_all$housefloor_material = as.factor(
    ifelse(housing_all$housefloor_material %in% c('1'),
        'concrete',
        ifelse(housing_all$housefloor_material %in% c('2','3','5','99'),'other','mud'))
)
housing_all$houseroof_material = as.factor(
    ifelse(housing_all$houseroof_material %in% c('2'), 'tin','other'))

housing_all$housewall_material = as.factor(
    ifelse(housing_all$housewall_material %in% c('1'),
        'concrete',
        ifelse(housing_all$housewall_material %in% c('3','4','5','8'),'other','tin'))
)

# remove variables 
housing_all <- housing_all %>% select(-rent_paid, 
                                          -housewall_material_other,
                                          -housefloor_material_other,
                                          -houseroof_material_other,
                                          -house_supply_off,
                                          -house_elec_cost,
                                          -lighting_source_other,
                                          -lighting_source,
                                          -latrine_other,
                                          -latrine_type,
                                          -drinking_other,
                                          -water_other,
                                          -water_purify,
                                          -water_other_purpose, # not informative
                                          -drinking_source,
                                          -water_purify_other,
                                          -arsenic_check,
                                          -color_check,
                                          -handpump,
                                          -garbage_other,
                                          -garbage,
                                          -fuel_source,
                                          -fuel_source_other)
# check NAs
map(housing_all, ~sum(is.na(.)))

# check data format types
# str(housing_all)

#################
# order factor variables
#################
# house wall, roof, and floor
housing_all$housewall_material <- factor(housing_all$housewall_material, ordered = TRUE,
                                         levels = c("concrete","tin","other"))
housing_all$houseroof_material <- factor(housing_all$houseroof_material, ordered = TRUE,
                                         levels = c("tin","other"))
housing_all$housefloor_material <- factor(housing_all$housefloor_material, ordered = TRUE,
                                          levels = c("concrete","mud","other"))

# > table(housing_all$houseroof_material)
#   1   2   3   4   5   6   7 
#   9 238   9   3  73   1   2 

# > table(housing_all$housewall_material)
#   1   2   3   4   5   8 
# 159 115   9   9  42   1 

# > table(housing_all$housefloor_material)
#   1   2   3   4   5  99 
# 113   2   3 212   2   3 

##########
# factor variables
##########
housing_all$house_elec  <- factor(housing_all$house_elec)
housing_all$fuel_source_wood  <- factor(housing_all$fuel_source_wood)
housing_all$lighting_source_elec  <- factor(housing_all$lighting_source_elec)
housing_all$water_supply  <- factor(housing_all$water_supply)
housing_all$drinking_source_same <- factor(housing_all$drinking_source_same)
housing_all$does_water_purify <- factor(housing_all$does_water_purify)
housing_all$garbage_collected <- factor(housing_all$garbage_collected)

str(housing_all)
```

```{r}
####################################################
## Latrine and Water
####################################################

# select variables
latrine_all <- `87. latrineUse.dta` %>% select(hh_ID, submissiondate, use_lat, main_use, count_latrine, pct_open)

# main_use  - too many factor levels (change to flush or no flush)
temp <- c("1","2","3","4","5","6")
latrine_all$main_use_flush <- ifelse(grepl(paste(temp, collapse = "|"),latrine_all$main_use), 1, 0)
latrine_all <- latrine_all %>% select(-main_use)

# pct_open  - too many factor levels (change to defacate or doesn't defacate in public)
latrine_all$defecation_public <- ifelse(grepl("1",latrine_all$pct_open), 1, 0)
latrine_all <- latrine_all %>% select(-pct_open)

# remove outliers for latrine count
latrine_all <- latrine_all %>% filter(count_latrine >= 0 & count_latrine <= 10)

##########
# if there is a hh_ID duplicate, use the first entry
##########
latrine_all$submissiondate <- as.Date(latrine_all$submissiondate, "%b %d, %Y")
latrine_all <- setDT(latrine_all)[latrine_all[, .I[which.min(submissiondate)], by=hh_ID]$V1]
latrine_all <- latrine_all %>% select(-submissiondate)
##########

##########
# factor variables
##########

latrine_all$use_lat <- factor(latrine_all$use_lat)
latrine_all$main_use_flush <- factor(latrine_all$main_use_flush)
latrine_all$defecation_public <- factor(latrine_all$defecation_public)

# check for NAs
# map(latrine_all, ~sum(is.na(.)))

# merge datasets
housing_all <- merge(latrine_all, housing_all, by = c("hh_ID"))
#housing_all$hh_ID[duplicated(housing_all$hh_ID)]

str(housing_all)
```

```{r}
####################################################
## Non-agricultural enterprise
####################################################

# Anyone in household owned/operated any business in 12 months?
nonagricultural_enterprise <- `57. NonAgriculturalEnterprise_level_1.dta` %>% select(hh_ID, submissiondate, business)

##########
# if there is a hh_ID duplicate, use the first entry
##########
nonagricultural_enterprise$submissiondate <- as.Date(nonagricultural_enterprise$submissiondate, "%b %d, %Y")
nonagricultural_enterprise <- setDT(nonagricultural_enterprise)[nonagricultural_enterprise[, .I[which.min(submissiondate)], by=hh_ID]$V1]
nonagricultural_enterprise <- nonagricultural_enterprise %>% select(-submissiondate)
##########

##########
# factor variables
##########

nonagricultural_enterprise$business <- factor(nonagricultural_enterprise$business)

# merge with household characteristics
housing_all <- merge(nonagricultural_enterprise, housing_all, by = c("hh_ID"))
# housing_all$hh_ID[duplicated(housing_all$hh_ID)]
#str(housing_all)
```

```{r}
####################################################
## Facilities
####################################################

facilities <- `20. Facilities_level_1.dta` %>% select(hh_ID,submissiondate, facilities, fac_count)

# there are too many variations on the types of facilities visited, so change to:
# visits health centers, bazaar, local shops
facilities$visits_healthcenter <- ifelse(grepl("1",facilities$facilities), 1, 0)
facilities$visits_bazaar <- ifelse(grepl("6",facilities$facilities), 1, 0)
facilities$visits_localshop <- ifelse(grepl("5",facilities$facilities), 1, 0)
facilities <- facilities %>% select(-facilities)

##########
# if there is a hh_ID duplicate, use the first entry
##########
facilities$submissiondate <- as.Date(facilities$submissiondate, "%b %d, %Y")
facilities <- setDT(facilities)[facilities[, .I[which.min(submissiondate)], by=hh_ID]$V1]
facilities <- facilities %>% select(-submissiondate)
##########

##########
# factor variables
##########
facilities$visits_healthcenter <- factor(facilities$visits_healthcenter)
facilities$visits_bazaar <- factor(facilities$visits_bazaar)
facilities$visits_localshop <- factor(facilities$visits_localshop)

# merge with household characteristics
housing_all <- merge(facilities, housing_all, by = c("hh_ID"))
#str(housing_all)
#housing_all$hh_ID[duplicated(housing_all$hh_ID)]
```

```{r}
####################################################
## Farming Plots
####################################################

# merge plot datasets together
plots <- Plots_plot_level_2.dta # fix year
temp <- plots_level_1.dta %>% select(hh_ID, submissiondate, plot_1_ID, today) 
plots <- merge(plots, temp, by=c("hh_ID","plot_1_ID"))

# determine plot age
plots$today <- format(as.Date(plots$today, format="%b %d, %Y"),"%Y")
plots$yr_acq <- format(as.Date(plots$yr_acq, format="%b %d, %Y"),"%Y")  
plots$today <- as.numeric(plots$today)
plots$yr_acq <- as.numeric(plots$yr_acq)
plots$plot_age <- plots$today - plots$yr_acq 

# too many plot types (change to three types: homestead, cultivable, other)
plots$plot_type_homestead <- ifelse(grepl("1",plots$plot_type), 1, 0)
temp <- c("2","8")
plots$plot_type_cultivable_land_pond <- ifelse(grepl(paste(temp, collapse = "|"),plots$plot_type), 1, 0)
# temp <- c("3","4","5","6","7","9"," ")
# plots$plot_type_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$plot_type), 1, 0)

# who_owns - too many factor levels (change to three types)
plots$who_owns_male <- ifelse(grepl("1",plots$who_owns), 1, 0)
plots$who_owns_family <- ifelse(grepl("2",plots$who_owns), 1, 0)
# temp <- c("3","4","5","6")
# plots$who_owns_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_owns), 1, 0)

# who_owns_off - too many factor levels (change to three types)
plots$who_owns_off_male <- ifelse(grepl("1",plots$who_owns_off), 1, 0)
plots$who_owns_off_family <- ifelse(grepl("2",plots$who_owns_off), 1, 0)
# temp <- c("3","4","5","6")
# plots$who_owns_off_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_owns_off), 1, 0)
 
# who_decision - too many factor levels (change to three types)
plots$who_decision_male <- ifelse(grepl("1",plots$who_decision), 1, 0)
plots$who_decision_family <- ifelse(grepl("2",plots$who_decision), 1, 0)
# temp <- c("3","4","5","6")
# plots$who_decision_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_decision), 1, 0)

# who_responsible - not enough responses, didn't include

# who_dec_spd - too many factor levels (change to three types)
plots$who_dec_spd_male <- ifelse(grepl("1",plots$who_dec_spd), 1, 0)
plots$who_dec_spd_family <- ifelse(grepl("2",plots$who_dec_spd), 1, 0)
# temp <- c("3","4","5","6")
# plots$who_dec_spd_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_dec_spd), 1, 0)

# who_infra - too many factor levels (change to three types)
plots$who_infra_male <- ifelse(grepl("1",plots$who_infra), 1, 0)
plots$who_infra_family <- ifelse(grepl("2",plots$who_infra), 1, 0)
# temp <- c("3","4","5","6")
# plots$who_infra_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$who_infra), 1, 0)

# cur_opr_status - too many factor levels (change to three types)
plots$cur_opr_status_fallow <- ifelse(grepl("1",plots$cur_opr_status), 1, 0)
plots$cur_opr_status_own <- ifelse(grepl("2",plots$cur_opr_status), 1, 0)
# temp <- c("3","4","5","6","7","8","9","11")
# plots$cur_opr_status_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$cur_opr_status), 1, 0)

# how_acq  - too many factor levels (change to three types)
plots$how_acq_bought <- ifelse(grepl("1",plots$how_acq), 1, 0)
plots$how_acq_inherited <- ifelse(grepl("2",plots$how_acq), 1, 0)
# temp <- c("3","4","5","6")
# plots$how_acq_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$how_acq), 1, 0)

# plot_use  - too many factor levels (change to four types)
plots$plot_use_agriculture <- ifelse(grepl("1",plots$plot_use), 1, 0)
plots$plot_use_fisheries <- ifelse(grepl("2",plots$plot_use), 1, 0)
plots$plot_use_livestock <- ifelse(grepl("2",plots$plot_use), 1, 0)
# temp <- c("3","4","5","6","7","99")
# plots$plot_use_other <- ifelse(grepl(paste(temp, collapse = "|"),plots$plot_use), 1, 0)

##########
# if there is a hh_ID duplicate, use the first entry
##########
# 100+ duplicates
plots$hh_ID[duplicated(plots$hh_ID)]
plots$submissiondate <- as.Date(plots$submissiondate, "%b %d, %Y")
plots <- setDT(plots)[plots[, .I[which.min(submissiondate)], by=hh_ID]$V1]
plots <- plots %>% select(-submissiondate)
##########

# select final variables
plots <- plots %>%  select( hh_ID,
                            plot_type_homestead,
                            plot_type_cultivable_land_pond,
                            #plot_type_other,
                            size_plot,
                            flood_depth, # wrong units probably
                            dis_from_home,
                            soil_type,
                            cur_opr_status_fallow,
                            cur_opr_status_own,
                            #cur_opr_status_other,
                            #amt_rec, too many NAs
                            cur_mv,
                            how_acq_bought,
                            how_acq_inherited,
                            #how_acq_other,
                            plot_age,
                            plot_use_agriculture,
                            plot_use_fisheries,
                            plot_use_livestock,
                            #plot_use_other,
                            #work_last_seas,  too many NAs
                            # In last 12 months, who decided to build any infrastructure on this plot?
                            who_infra_male,
                            who_infra_family,
                            #who_infra_other,
                            # Who uses the plot?  
                            who_owns_male,
                            who_owns_family,
                            #who_owns_other,
                            # Who officially owns?
                            who_owns_off_male,
                            who_owns_off_family,
                            #who_owns_off_other,
                            # who_decision who takes most decisions regarding type of crop to be planted or fish to be raised?
                            who_decision_male,
                            who_decision_family,
                            #who_decision_other,
                            # who decides how to spend revenues generated from crops or fish?
                            who_dec_spd_male,
                            who_dec_spd_family)
                            #who_dec_spd_other)

##########
# factor variables
##########
plots$plot_type_homestead <- factor(plots$plot_type_homestead)
plots$plot_type_cultivable_land_pond <- factor(plots$plot_type_cultivable_land_pond)
plots$soil_type <- factor(plots$soil_type)
plots$cur_opr_status_fallow <- factor(plots$cur_opr_status_fallow)
plots$cur_opr_status_own <- factor(plots$cur_opr_status_own)
plots$how_acq_bought <- factor(plots$how_acq_bought)
plots$how_acq_inherited <- factor(plots$how_acq_inherited)
plots$plot_use_agriculture <- factor(plots$plot_use_agriculture)
plots$plot_use_fisheries <- factor(plots$plot_use_fisheries)
plots$plot_use_livestock <- factor(plots$plot_use_livestock)
plots$who_infra_male <- factor(plots$who_infra_male)
plots$who_infra_family <- factor(plots$who_infra_family)
plots$who_owns_male <- factor(plots$who_owns_male)
plots$who_owns_family <- factor(plots$who_owns_family)
plots$who_owns_off_male <- factor(plots$who_owns_off_male)
plots$who_owns_off_family <- factor(plots$who_owns_off_family)
plots$who_decision_male <- factor(plots$who_decision_male)
plots$who_decision_family <- factor(plots$who_decision_family)
plots$who_dec_spd_male <- factor(plots$who_dec_spd_male)
plots$who_dec_spd_family <- factor(plots$who_dec_spd_family)

# check for NAs
# map(plots, ~sum(is.na(.)))

# merge with household characteristics
housing_all <- merge(plots, housing_all, by = c("hh_ID"))
#housing_all$hh_ID[duplicated(housing_all$hh_ID)]
str(housing_all)
```

```{r}
# merge datasets
hh_data <- merge(housing_all, hh_char, by = "hh_ID")
str(hh_data)
#hh_data$hh_ID[duplicated(hh_data$hh_ID)]

#########################################################
# Separate categorical variables and continuous variables
#########################################################
categorical_variables <- hh_data %>% select(-size_plot, 
                                            -flood_depth, 
                                            -dis_from_home, 
                                            -cur_mv, 
                                            -plot_age, 
                                            -fac_count,
                                            -count_latrine, 
                                            -rent_estimate, 
                                            -house_age,
                                            -rent_estimate,
                                            -house_rooms, 
                                            -house_rooms_sleeping,
                                            -house_sharing,
                                            -house_age, 
                                            -fuel_cost, 
                                            -lighting_cost, 
                                            -cell_cost, 
                                            -cellphone,
                                            -fac_count,
                                            -numChildren,
                                            -pctCanCarry20L,
                                            -pctCanWalk5Km,
                                            -pctCanStandOwn,
                                            -hh_members)
continuous_variables <- hh_data %>% select(hh_ID,
                                           size_plot, 
                                            flood_depth, 
                                            dis_from_home, 
                                            cur_mv, 
                                            plot_age, 
                                            fac_count,
                                            count_latrine, 
                                            rent_estimate, 
                                            house_age,
                                            rent_estimate,
                                            house_rooms, 
                                            house_rooms_sleeping,
                                            house_sharing,
                                            house_age, 
                                            fuel_cost, 
                                            lighting_cost, 
                                            cell_cost, 
                                            cellphone,
                                            fac_count,
                                            numChildren,
                                            pctCanCarry20L,
                                            pctCanWalk5Km,
                                            pctCanStandOwn,
                                            hh_members)

# scale continuous variables
continuous_variables1 <- apply(continuous_variables[,2:22], 2, scale)
continuous_variables <- data.frame(continuous_variables1,continuous_variables$hh_ID)
continuous_variables <- continuous_variables %>% mutate(hh_ID = continuous_variables.hh_ID) %>% select(-continuous_variables.hh_ID)

##################################
# combine continous and categorical into one dataset
##################################

# merge categorical and continous variables into one dataframe
final_hh_data <- merge(categorical_variables, continuous_variables, by ="hh_ID")

# remove NAs
final_hh_data_noNAs <- final_hh_data[complete.cases(final_hh_data),]
# recode dummy frame
final_hh_data_noNAs <- dummy.data.frame(final_hh_data_noNAs)
```

# PCA

# Figure out dimensions of well-being using Factor Analysis

http://www.di.fc.ul.pt/~jpn/r/factoranalysis/factoranalysis.html#factor-analysis-vs.pca

# Food Diary
```{r}

# Which of the following groups of foods were consumed by members of your household in the last ${recall_length} hours?
# Scroll carefully down the list and select all that apply.

# select noncrowdsourced data
fooddiary_1 <- `33.FoodDiary_level_1.dta` %>% filter(crowdsource==0)

# select variables
fooddiary_1 <- fooddiary_1 %>% select(hh_ID, 
                                      food_1_ID,
                                      submissiondate, 
                                      recall, # month 516 season 272 week 4944
                                      week_number, #3:50 weeks
                                      # gender, 
                                      # age, 
                                      # education, 
                                      # highest_class, 
                                      # relationship, 
                                      food_list, # groups of foods consumed
                                      food_count) # number of foods selected
fooddiary_2 <- `34. FoodDiary_food_level_2.dta` %>% select(hh_ID, 
                                      food_1_ID,
                                      food_2_ID,
                                      food_grp_namec, 
                                      food_type) #will require grepl
fooddiary_3 <- `35. Fooddiary_food_foodtype_level_3.dta` %>% select(hh_ID, 
                                      food_2_ID,
                                      food_3_ID,
                                      food_ID = food_type_name, 
                                      food_type_quant,
                                      food_type_unit,
                                      quant_pur, #How much consumed was purchased?
                                      quant_own, #How much consumed was own production?
                                      quant_other) #How much consumed was from other sources?

# duplicate rows based on food_count - not necessary
# fooddiary_1 <- fooddiary_1[rep(seq(nrow(fooddiary_1)), fooddiary_1$food_count),]

# merge levels 1 and 2
fooddiary_1_2 <- merge(fooddiary_1,fooddiary_2, by=c("hh_ID","food_1_ID"))

# merge with level 3
fooddiary_all <- merge(fooddiary_1_2,fooddiary_3, by=c("hh_ID","food_2_ID"))

# remove unwanted variables
fooddiary_all <- fooddiary_all %>% select(-food_1_ID,-food_2_ID,-food_3_ID,-food_type)

# 118 food_type_name are missing
# map(fooddiary_all, ~sum(is.na(.)))
# remove missing values for now.
fooddiary_all <- fooddiary_all[complete.cases(fooddiary_all),]
```

*Food Type Unit*
9,262 1 Kg
8,285 2 Grams
205 3 Liter
308 4 Milliliter
591 5 Tablespoon
391 6 Teaspoon
208 7 Drops
3,088 8 Count

```{r}
# food names
food_list <- read_csv("Datasets/food_list.csv")
food_calories <- read_csv("Datasets/food_cal.csv")
food_calories <- food_calories %>% mutate(food_name = food_type)  %>% 
                                   select(-food_type)
food_info <- merge(food_calories, food_list, by="food_name")

##############################
# some calories are zero, fix?????????
##############################
# Carbohydrates provide 4 calories per gram, protein provides 4 calories per gram, and fat provides 9 calories per gram
# food_info <- food_info %>% filter(calorie_grams != 0)

# merge with food list names 
fooddiary_cleaned <- merge(food_info, fooddiary_all, by="food_ID")
fooddiary_cleaned <- fooddiary_cleaned %>% select(hh_ID,
                                                  submissiondate,
                                                  recall,
                                                  week_number,
                                                  food_ID,
                                                  food_count,
                                                  food_name,
                                                  food_name_type,
                                                  food_type_quant,
                                                  food_type_unit,
                                                  quant_pur,
                                                  quant_own,
                                                  quant_other)

# percent purchased, grown, other
fooddiary_cleaned <- fooddiary_cleaned %>% mutate(quant_pur_pct = quant_pur/food_type_quant,
                                                  quant_own_pct = quant_own/food_type_quant,
                                                  quant_other_pct = quant_other/food_type_quant)

# merge with food calories/info
fooddiary_cleaned <- merge(fooddiary_cleaned, food_info, by=c("food_ID","food_name_type","food_name"))

# reorder variables
fooddiary_cleaned <- fooddiary_cleaned %>% select(hh_ID,
                                                  submissiondate,
                                                  recall,
                                                  week_number,
                                                  food_ID,
                                                  food_count,
                                                  food_name,
                                                  food_name_type,
                                                  food_type_quant,
                                                  food_type_unit,
                                                  calories_grams,
                                                  quant_pur,
                                                  quant_own,
                                                  quant_other,
                                                  quant_pur_pct,
                                                  quant_own_pct,
                                                  quant_other_pct)

# fix dates and times
fooddiary_cleaned <- fooddiary_cleaned %>%
  mutate(datetime = as.POSIXct(strptime(submissiondate, format = "%b %d, %Y %I:%M:%S %p")),
         datetime_military = strftime(datetime, format = "%Y-%m-%d %H:%M"))

# extract month
fooddiary_cleaned$submission_month <- month(fooddiary_cleaned$datetime)
# extract weekday
fooddiary_cleaned$submission_weekday <- weekdays(fooddiary_cleaned$datetime)
# create breaks

# time of day
breaks <- hour(hm("00:00", "6:00", "12:00", "18:00", "23:59"))
# labels for the breaks
labels <- c("Night", "Morning", "Afternoon", "Evening")
fooddiary_cleaned$time_of_day <- cut(x=hour(fooddiary_cleaned$datetime), 
                                     breaks = breaks, 
                                     labels = labels, include.lowest=TRUE)
```

*Calculate average caloric intake per person in each household*
```{r fig1, fig.height = 4, fig.width = 4}
# 1	Kg          *1000
# 2	Grams
# 3	Liter       *1000
# 4	Milliliter  /1000
# 5	Tablespoon  *15
# 6	Teaspoon    *4.2
# 7	Drops       *0.05
# 8	Count

# unit conversions
fooddiary_cleaned <- fooddiary_cleaned %>% 
  mutate(calories_total_grams = case_when((food_type_unit==1) ~ calories_grams*(food_type_quant*1000),
                                          (food_type_unit==2) ~ calories_grams*food_type_quant,
                                          (food_type_unit==3) ~ calories_grams*(food_type_quant*1000),
                                          (food_type_unit==4) ~ calories_grams*(food_type_quant/1000),
                                          (food_type_unit==5) ~ calories_grams*food_type_quant,
                                          (food_type_unit==6) ~ calories_grams*(food_type_quant*4.2),
                                          (food_type_unit==7) ~ calories_grams*(food_type_quant*0.05)))

#####################################
# fix food units claimed as "counts"
#####################################
fooddiary_cleaned_count <- fooddiary_cleaned %>% filter(food_type_unit == 8) %>% arrange(desc(food_name_type))

# grains (changed to kg)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Parboiled rice (coarse)") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Fine rice") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Atta") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Non-parboiled rice (coarse)") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Semai/noodles") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Chira (flattened rice)") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Muri/Khoi (puffed rice)") ~ calories_grams*(food_type_quant*1000)))
# meats (mostly changed to kg)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Beef/buffalo") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Mutton") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Chicken") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Pigeon") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Fish egg") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Egg") ~ calories_grams*(food_type_quant*50), # egg weighs 50g
                                                (food_name=="Duck") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Stomach of beef/goat") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Dried meat") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Bids/bok/gughu") ~ calories_grams*(food_type_quant*1000),
                                                (food_name=="Liver") ~ calories_grams*(food_type_quant*1000)))

# oil (changed to 15ml)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Soybean") ~ calories_grams*(food_type_quant*15),
                                                (food_name=="Mustard") ~ calories_grams*(food_type_quant*15),
                                                (food_name=="Dalda/banspati") ~ calories_grams*(food_type_quant*15),
                                                (food_name=="Red Palm Oil") ~ calories_grams*(food_type_quant*15),
                                                (food_name=="Ghee") ~ calories_grams*(food_type_quant*15),
                                                (food_name=="Sesame oil") ~ calories_grams*(food_type_quant*15), 
                                                (food_name=="Yellow Palm Oil") ~ calories_grams*(food_type_quant*15)))
# drinks/dairy (can = 340grams/12 fl oz)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Tea –prepared") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Coke/ Seven-up etc/Pepci/RC/Urocola etc") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Milk") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Milk in Tea") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Powdered Milk") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Condensed Milk") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Butter") ~ calories_grams*(food_type_quant*113), # serving of butter
                                                (food_name=="Yogurt") ~ calories_grams*(food_type_quant*340),
                                                (food_name=="Cottage cheese or Paneer") ~ calories_grams*(food_type_quant*340), 
                                                (food_name=="Buttermilk") ~ calories_grams*(food_type_quant*340), 
                                                (food_name=="Solid Cheese Curds") ~ calories_grams*(food_type_quant*340), 
                                                (food_name=="Ice Cream") ~ calories_grams*(food_type_quant*340)))
           

# fish small (avg  small calorie count 340)
# some gura mach in 500 for quantity.....fix later???????
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Gura mach") ~ food_type_quant*340,
                                                 (food_name=="Panch mishali") ~ food_type_quant*340,
                                                 (food_name=="Palshe") ~ food_type_quant*340,
                                                 (food_name=="Tatkeni") ~ food_type_quant*340,
                                                 (food_name=="Puti") ~ food_type_quant*340,
                                                 (food_name=="Tengra") ~ food_type_quant*340,
                                                 (food_name=="Karfu fish") ~ food_type_quant*340,
                                                 (food_name=="Bata") ~ food_type_quant*340,
                                                 (food_name=="Kajari") ~ food_type_quant*340,
                                                 (food_name=="Small prawn") ~ food_type_quant*340,
                                                 (food_name=="Dried small shrimp/prawn") ~ food_type_quant*340))

# fish large (avg large fish calorie count 510)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Rui") ~ food_type_quant*510,
                                                 (food_name=="Telapia") ~ food_type_quant*510,
                                                 (food_name=="Swarputi") ~ food_type_quant*510,
                                                 (food_name=="Singi") ~ food_type_quant*510,
                                                 (food_name=="Grass Carp") ~ food_type_quant*510,
                                                 (food_name=="Taki") ~ food_type_quant*510,
                                                 (food_name=="Pangash") ~ food_type_quant*510,
                                                 (food_name=="Silver Carp") ~ food_type_quant*510,
                                                 (food_name=="Mrigel") ~ food_type_quant*510,
                                                 (food_name=="Kalibaus") ~ food_type_quant*510,
                                                 (food_name=="Hilsa") ~ food_type_quant*510,
                                                 (food_name=="Katla") ~ food_type_quant*510,
                                                 (food_name=="Jatka") ~ food_type_quant*510,
                                                 (food_name=="Aair") ~ food_type_quant*510,
                                                 (food_name=="Boal") ~ food_type_quant*510,
                                                 (food_name=="Dried fish") ~ food_type_quant*510,
                                                 (food_name=="Mirror Carp") ~ food_type_quant*510))

# fix vegetables
"Patal"                                   "Okra"                                    "Eggplant"                               
"Bitter gourd"                            "Radish"                                  "Pumpkin"                                
"Green chili"                             "Potato"                                  "Sheem"                                  
"Onion"                                   "Tomato"                                  "Sweet gourd"                            
"Garlic"                                  "Water gourd"                             "Drum stick"                             
"Carrot"                                  "Green banana"                            "Cauliflower"                            
"Danta (amaranth)"                        "Green Papaya"                            "Ash gourd"                              
"Cucumber"                                "Kachu (arum)"                            "Sweet potato"                           
"Green mango"                             "Dhundal"                                 "Kachur lati"                            
"Green pea"                               "Green jackfruit"                         "Mete alu"                               
"Beher gura"                              "Soybean bori"                            "Kakrol"                                 
"Shalgom"                                 

# spices (avg calorie count 5)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Dried chili") ~ food_type_quant*5,
                                                 (food_name=="Elachi") ~ food_type_quant*5,
                                                 (food_name=="Cinnamon") ~ food_type_quant*5,
                                                 (food_name=="Fresh Ginger") ~ food_type_quant*5))

# pulses (avg calorie count 160)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name=="Khesari") ~ food_type_quant*160,
                                                 (food_name=="Shem bitchi") ~ food_type_quant*160,
                                                 (food_name=="Anchor daal") ~ food_type_quant*160,
                                                 (food_name=="Dried Chick pea") ~ food_type_quant*160,
                                                 (food_name=="Mung") ~ food_type_quant*160,
                                                 (food_name=="Black gram") ~ food_type_quant*160,
                                                 (food_name=="Dried Pea") ~ food_type_quant*160,
                                                 (food_name=="Groundnut") ~ food_type_quant*160,
                                                 (food_name=="Brazilnut") ~ food_type_quant*160,
                                                 (food_name=="Cashew Nut") ~ food_type_quant*160,
                                                 (food_name=="Almond/Badam") ~ food_type_quant*160,
                                                 (food_name=="Hazelnut") ~ food_type_quant*160,
                                                 (food_name=="Chestnut") ~ food_type_quant*160))

# other food (50 for now)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name_type=="otherfoodohome") ~ food_type_quant*50))
# "Pitha"                                   "Ruti/Parota"                            
# "Rice/Jao"                                "Singara"                                 "Piaju"                                  
# "Cake"                                    "Nimki"                                   "Puri"                                   
# "Alur chap"                               "Biscuit"                                 "Bonroti/paoroti"                        
# "Polao/Biryani/Tehari"                    "Patties"                                 "Khichuri"                               
# "Chips"                                   "Chewing gum"                                                          

# other food (50 for now)
fooddiary_cleaned_count <- fooddiary_cleaned_count %>% 
  dplyr::mutate(calories_total_grams = case_when((food_name_type=="vegetables") ~ food_type_quant*50))                       
# vegetables
"Lal Shak (red amaranth)"                 "Bathua"                                  "Pat Shak"
"Dheki Shak"                              "Pui (Indian spinach)"                    "Dhania Shak"                            
"Lau Shak"                                "Onion/garlic stalk"                      "Kalmi Shak"                             
"Kachu Shak"                              "Kalo kachu Shak"                         "Radish leaves"                          
"Cabbage"                                 "Helencha"                                "Katanate"                               
"Palang Shak (spinach)"                   "Pea leaves"                              "Drumstick leaves"                       
"Mustard leaves"                          "Mixed leafy vegetables"                  "Dudhali Pata"                           
"Black gram leaves"                       "Swett gourd leaves"                      "Khesari Shak"                           
"Geema Shak"                              "Neem Shak"                               "Darkuni Shak"                           
"Bokful"                                  "Litchis"                                 

# fruit
"Apple"                                  
"Karambola"                               "Mango"                                   "Banana"                                 
"Grapes"                                  "Guava"                                   "Lemon"                                  
"Jujube/dried jujube"                     "Dates"                                   "Orange"                                 
"Olive"                                   "Coconut"                                 "Bel"                                    
"Amra"                                    "Chalta"                                  "Green Coconut"                          
"Papaya"                                  "Jack Fruit"                              "Ata (bullock's heart)"                  
"Black berry"                             "Pomelo"                                  "Tamarind"                               
"Dalim"                                   "Tarmuj (Water melon)"                    "Bangi (Musk melon)"                     
"Pine apple"                              "Sobeda"                                  "Jaamrul"                                

# sensativity analysis  
# cluster 
```


## Plots
```{r}
fooddiary_nocounts <- fooddiary_cleaned %>% filter(food_type_unit != 8) %>% filter(recall=="week")

p1 <- ggplot(fooddiary_nocounts, aes(x=submission_month, y=calories_total_grams)) +
  geom_line(color="#69b3a2", size=2) +
  ggtitle("Calories reported by month")

p2 <- ggplot(fooddiary_nocounts, aes(x=week_number, y=calories_total_grams)) +
  geom_line(color="#69b3a2", size=2) +
  ggtitle("Calories reported by week")

p3 <- ggplot(fooddiary_nocounts, aes(x=time_of_day, y=calories_total_grams)) +
  geom_line(color="#69b3a2", size=2) +
  ggtitle("Calories reported by time of day")

p4 <- ggplot(fooddiary_nocounts, aes(x=submission_weekday, y=calories_total_grams)) +
  geom_line(color="#69b3a2", size=2) +
  ggtitle("Calories reported by day of the week")

p1
p2
p3
p4
```
```{r fig1, fig.height = 3.5, fig.width = 3.5}
p1 <- fooddiary_nocounts %>%
  filter(recall=="week") %>%
  ggplot(aes(food_name_type)) +
      geom_bar(fill = "darkorchid4") +
      facet_wrap( ~ submission_month, ncol = 4) +
      labs(title = "Food Types Reported by Week",
           subtitle = " ",
           y = "count",
           x = "food group") + theme_bw(base_size = 15)
p1 + theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

Look for Ramadan and Manga
```{r fig2, fig.height = 3.5, fig.width = 3.5}
# fooddiary_cleaned <- fooddiary_cleaned %>% mutate(calories_total_kg = calories_total_grams/1000)

fooddiary_cleaned_week <- fooddiary_nocounts 
xyplot(
  calories_total_grams ~ submission_month | food_name_type, 
  # layout = c(2, 7),               # panel with ncol = 5 and nrow = 3
  group = food_name_type, data = fooddiary_cleaned_week,
  type = c("p", "smooth"),        # Show points and smoothed line
  scales = "free"                 # Make panels axis scales independent
  )
```

# Notes
Responses in food diary:
Look over time and identify periods were there were responses
Seasonal access to calories
Mean and variance as access to calories and cluster households
Relatively low caloric variation/or feast vs famine
